\section{Bayesian Trust Network}
To assess our trust in the other peers in the system, we implemented the model
from ``B-trust: Bayesian Trust Framework for Pervasive Computing''
\cite{btrust}. The paper describes a method of maintaining context-sensitive
information about previous direct experiences with other peers as well as
the recommended trust received from third-party recommenders. Trust values
are stored probabilistically and trust evolution from one
experience/recommendation to another uses a form a Bayes' theorem.

For each context and peer, we store a vector that represents a discrete
probability mass function (pmf) of our direct trust $d_\alpha$, which is the
trust formed from previous direct experiences with this peer. We similarly store a
vector for the recommended trust pmf $r_\alpha$, which is the trust formed from
recommendations received about this peer from third-parties.

Again for each context and peer, we store two matrices (direct and recommended)
which govern the evolution of trust. By scaling the feedback when the trust
pmfs evolve, these matrices control how much the pmfs change when we receive
additional information about a peer. In terms of Bayes' theorem, the
values in these matrices are conditional probabilities which act as weights
to the prior probabilities of the trust level.

These pmfs are initialized to the uniform discrete distribution, which
represents a lack of information about this peer's behaviour. After a few rounds
of trust evolution, the mean $\mu_{\{d,r\}}$ of this pmf \eqref{eq:bayes_mean}
is a single value representing our direct/recommended trust in a given peer,
while the variance $\sigma^2_{\{d,r\}}$ of the pmf \eqref{eq:bayes_variance}
represents our confidence in this trust value. The uniform discrete distribution
has the highest variance $\sigma^2_U = \frac{n^2-1}{12}$, while the degenerate
distribution has the lowest $\sigma^2_\delta = 0$, so we map this variance range
into a confidence value on [0,1] using \eqref{eq:bayes_confidence}.

\begin{equation}
\label{eq:bayes_mean}
\mu_{\{d,r\}} = \sum_{i=0}^{n-1}{i*{\{d,r\}}_i}
\end{equation}

\begin{equation}
\label{eq:bayes_variance}
\sigma^2_{\{d,r\}} = \sum_{i=0}^{n-1}{i^2*{\{d,r\}}_i} - \mu^2_{\{d,r\}}
\end{equation}

\begin{equation}
\label{eq:bayes_confidence}
c = 1 - \frac{\sigma^2_{\{d,r\}}}{\sigma^2_U}}
\end{equation}
